---
title: "HAR Prediction Model via randomForest"
author: "Pranjal Mandhaniya"
date: "Sunday 25 January 2015"
output: html_document
---

### Firstly reading input from csv files

```{r,cache=TRUE,message=FALSE}
library(RCurl)
train <- read.csv(text = getURL("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"))
test <- read.csv(text = getURL("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"))

```

### Put some scaling efforts to get useful but small formula.

```{r,cache=TRUE}
# Remove NA and empty columns because they most probably won't affect much.
nt <- train[ , (colSums(is.na(train)) == 0)&(colSums(train == "") == 0)]

```{r,message=F,cache=TRUE}
library(dplyr)
```
```{r,cache=TRUE}
# Selecting only numeric and integer columns plus classe column. 
ndt <- select(nt,num_window:classe) 
```

### Check for useful variables which change significantly w.r.t classe.

```{r,cache=TRUE,warning=FALSE}
# Aggregate cleaned data for coefficient of variation wrt each classe.
abscov <- aggregate(.~classe,data = ndt,FUN = function(x){abs(sd(x)/mean(x))})

# Check columnwise coefficient of variation.
covcol <- data.frame(sapply(abscov,FUN = function(x){abs(sd(x)/mean(x))}),names(abscov))

# Filter those columns whose C.o.V is greater than 1 i.e. significant.
needed <- covcol[(covcol[,1]>1),]

# From main data i.e train , select significant columns.
pred <- train[,(names(train) %in% as.character(unlist(needed[2])))|(names(train)=="classe")]
```

### Fitting model by randomForest and Prediction.
```{r,cache=TRUE}
# Use randomForest and set seed for reproducible results.
```{r,message=F,cache=TRUE}
library(randomForest)
```
```{r,cache=TRUE}
set.seed(33)

# Fit model on Scaled data frame and print output confusion matrix.
fit <- randomForest(classe~., data=pred, importance=TRUE, ntree=2000)
fit

# Predict test data with above formula.
prediction <- predict(fit, test)
prediction
```

### Writing files within a folder
```{r,cache=TRUE}
# Function to write files.
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

# Set and create a working directory folder.
mndir <- getwd()
sbdir <- "pml_ans"
dir.create(file.path(mndir, sbdir), showWarnings = FALSE)
setwd(file.path(mndir, sbdir))

# Writing in folder.
pml_write_files(prediction)
```
